Schema Evolution in Interactive Programming Systems

### 2024-08-23 paper.tex
Clarify not a concrete tool

Our primary contribution is a suite of challenge problems that exemplify a diverse range of typical schema change scenarios which interrupt feedback loops. We believe these problems have not been completely solved in theory or practice (see \S\ref{sec:related}  Related Work). While some of these problems come from our individual research efforts we have attempted to make neutral problem statements not slanted to our preferred approaches. We propose these challenge problems to motivate and facilitate further research. We hope they serve as examples to ground such research and as a basis for evaluating results. We invite contributions of further challenge problems and look forward to discussing competing solutions.

>>>>

Our primary contribution is a suite of challenge problems exemplifying a diverse range of typical schema change scenarios that interrupt feedback loops. We believe these problems have not been completely solved in theory or practice (see \S\ref{sec:related} Related Work). While some of these problems come from our individual research efforts we have attempted to make neutral problem statements not slanted to our preferred approaches. None of our ongoing efforts yet address the full range of problems. Indeed the motivation of this paper is to provide a basis for communicating and collaborating between related efforts, not to mention motivating further research efforts. We hope these challange problems serve as examples to ground future research and as a basis for evaluating the results. We invite contributions of new challenge problems and look forward to discussing competing solutions.
